\documentclass{article}
\usepackage{parskip} % For consistent spacing
\usepackage{enumitem} % For customizing lists
\usepackage{xcolor} % For color

\begin{document}

\title{Arithmetic Sequences Practice Questions}
\author{}
\date{}
\maketitle

\begin{enumerate}[itemsep=2em] % itemsep sets space between items
    % Recursive Formula Questions
    \item Given the sequence $5, 8, 11, \ldots$ What is the next term? \\
    \textcolor{red}{$14$}
    
    \item If an arithmetic sequence starts with $2$ and has a common difference of $3$, what is the $3$rd term? \\
    \textcolor{red}{$8$}
    
    \item The sequence $-1, 2, 5, \ldots$ is defined by which recursive formula? \\
    \textcolor{red}{$a_n = a_{n-1} + 3$}
    
    \item An arithmetic sequence is defined by $a_n = a_{n-1} + 4$. If $a_5 = 33$, what is $a_1$? \\
    \textcolor{red}{$a_1 = 17$}
    
    \item The sequence starts with $-4$ and the $5$th term is $16$. What is the recursive formula for the sequence? \\
    \textcolor{red}{$a_n = a_{n-1} + 5$}
    
    \item If the third term of an arithmetic sequence is $14$ and the fifth term is $22$, determine the recursive formula. \\
    \textcolor{red}{$a_n = a_{n-1} + 4$}
    
    \item An arithmetic sequence is defined by $a_n = a_{n-1} - 6$. If $a_7 = -35$, determine $a_2$. \\
    \textcolor{red}{$a_2 = -5$}
    
    \item The $8$th term of an arithmetic sequence is $50$, and the $10$th term is $70$. Define the recursive formula for the sequence. \\
    \textcolor{red}{$a_n = a_{n-1} + 10$}
    
    \item If $a_3 = 6$ and $a_5 = 18$ in an arithmetic sequence, what is the value of $a_1$? \\
    \textcolor{red}{$a_1 = -6$}

    % Explicit Formula Questions
    \item Given the sequence $3, 5, 7, \ldots$ What is the explicit formula? \\
    \textcolor{red}{$a_n = 2n + 1$}
    
    \item What is the $7$th term of the sequence defined by $a_n = 2n + 1$? \\
    \textcolor{red}{$15$}
    
    \item For the sequence $a_n = 3n - 2$, determine $a_5$. \\
    \textcolor{red}{$13$}
    
    \item A sequence starts with $5$ and has a common difference of $-3$. What is the explicit formula? \\
    \textcolor{red}{$a_n = -3n + 8$}
    
    \item The $4$th term of an arithmetic sequence is $16$ and the $7$th term is $28$. Find the explicit formula. \\
    \textcolor{red}{$a_n = 4n + 4$}
    
    \item If the explicit formula of a sequence is $a_n = -4n + 10$, what is the common difference? \\
    \textcolor{red}{$-4$}
    
    \item Given $a_5 = 23$ and $a_8 = 41$, determine the explicit formula of the sequence. \\
    \textcolor{red}{$a_n = 6n + 5$}
    
    \item If $a_1 = 3$ and $a_10 = -57$, what is the explicit formula for the arithmetic sequence? \\
    \textcolor{red}{$a_n = -6n + 9$}
    
    \item An arithmetic sequence has its $6$th term as $45$ and $11$th term as $80$. Find the explicit formula. \\
    \textcolor{red}{$a_n = 7n + 3$}
\end{enumerate}

\end{document}
